How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-20 Paper/paper.tex
slightly changed title and fixed use of latex commands (add tilde)

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1sprites}
	\caption{Histogram of the number of sprites in the analyzed projects}
	\label{fig:size-sprites}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1scripts}
	\caption{Histogram of the number of scripts in the analyzed projects}
	\label{fig:size-scripts}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1locs}
	\caption{Histogram of the lines of code in the analyzed projects}
	\label{fig:size-locs}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1indent}
	\caption{Histogram of the maximum code indentation level in the analyzed projects}
	\label{fig:size-indent}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/3cyclomatic}
	\caption{Histogram of the McCabe cyclomatic complexity of the \nscripts analyzed scripts}
	\label{fig:cyclomatic}
\end{figure}

In Table \ref{tbl-size} we summarize statistics for metrics related to size and complexity. We use the mean value and the five-number summary to describe the dataset in terms of the number of sprites with code per project (including the stage sprite) and the number of scripts per project, where each script is a code-block of interconnected Scratch blocks. For example, in Figure \ref{fig:ui} the cat sprite contains 2 scripts. We further measure the lines of code per project, considering each Scratch block to represent exactly one line of code, thus not counting the closing constructs of loops or conditional statements as separate lines. The maximum code indentation level is used as a code complexity metric. It was calculated using the JSON array depth? \todo{felienne, how did we measure this?}. This corresponds to code indentation level returning 1 for all first-level blocks and increasing by 2 for block enclosures in loops or conditional statements. Figures \ref{fig:size-sprites}, \ref{fig:size-scripts}, \ref{fig:size-locs} and \ref{fig:size-indent} plot the distribution of those size metrics.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1sprites}
	\caption{Histogram of the number of sprites in the analyzed projects}
	\label{fig:size-sprites}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1scripts}
	\caption{Histogram of the number of scripts in the analyzed projects}
	\label{fig:size-scripts}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1locs}
	\caption{Histogram of the lines of code in the analyzed projects}
	\label{fig:size-locs}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1indent}
	\caption{Histogram of the maximum code indentation level in the analyzed projects}
	\label{fig:size-indent}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/3cyclomatic}
	\caption{Histogram of the McCabe cyclomatic complexity of the \nscripts~analyzed scripts}
	\label{fig:cyclomatic}
\end{figure}

In Table \ref{tbl-size} we summarize statistics for metrics related to size and complexity. We use the mean value and the five-number summary to describe the dataset in terms of the number of sprites with code per project (including the stage sprite) and the number of scripts per project, where each script is a code-block of interconnected Scratch blocks. For example, in Figure \ref{fig:ui} the cat sprite contains two scripts. We further measure the lines of code per project, considering each Scratch block to represent exactly one line of code, thus not counting the closing constructs of loops or conditional statements as separate lines. The maximum code indentation level is used as a code complexity metric. It was calculated using the JSON array depth? \todo{felienne, how did we measure this?}. This corresponds to code indentation level returning 1 for all first-level blocks and increasing by 2 for block enclosures in loops or conditional statements. Figures \ref{fig:size-sprites}, \ref{fig:size-scripts}, \ref{fig:size-locs} and \ref{fig:size-indent} plot the distribution of those size metrics.
